%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

\let\tempone\itemize
\let\temptwo\enditemize
\renewenvironment{itemize}{\tempone\addtolength{\itemsep}{0.25\baselineskip}}{\temptwo}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Azamat Rsymbetov}
\address{53 Abay ave, Apt 36 \linebreak Almaty, KZ 050063}
\contacts{+7 (708) 646-4281 \linebreak seetwopluses@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Work Experience and Projects}
		\begin{cvsubsection}{Software Engineer, Intern}{Method Pro}{Summer 2019}
			\begin{itemize}
				\item Developed Amazon Alexa skill that checks Onay card balance using Node.js.
				\item Developed backend based on microservice architecture for online store prototype using Node.js and SQLite.
				\item Scraped data from Tengrinews and built backend for sentiment analysis project using Puppeteer.js and Node.js.
			\end{itemize}
		\end{cvsubsection}

    \begin{cvsubsection}{Scala Developer, Intern}{OneTechnologies}{Summer 2020}
			\begin{itemize}
        \item Developed Telegram Bot with NLP using Dialogflow that fetches data from Codeforces API
			\end{itemize}
		\end{cvsubsection}

    \begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{MathSnake} (2017). Classical Snake Game with modified rules, where the objective is to score certain amount of points using math. JavaScript, Canvas. 
				\item \textbf{Keylogger} (2018). CLI utility which runs in the background, records key presses to the logfile and sends it to a given email. Python.
        \item \textbf{LawyerFinder} (2018). Web app which helps to find and hire lawyers. JavaScript.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Education}
		\begin{cvsubsection}{Almaty, Kazakhstan}{Suleyman Demirel University}{2018 - 2022}
			\begin{itemize}
				\item B.Sc. in Computer Science.
        \item Coursework: Fundamentals of Programming, Database Management Systems, Advanced Algorithms, Prepartion for ACM, Calculus I, Calculus II, Linear Algebra
			\end{itemize}
		\end{cvsubsection}

    \begin{cvsubsection}{Ulsan, South Korea}{Ulsan National Institute of Science and Technology}{Fall 2019}
			\begin{itemize}
				\item Exchange Student, Computer Science.
				\item Coursework: Introduction to Algorithms, Computer Networks, Discrete Mathematics, Basic Circuit Theory, Probability and Introduction to Random Processes
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

  \begin{cvsection}{Additional Experience and Awards}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Participation, IITU Robocon 2015} Built robots based on Arduino. Implemented line detection and robot control algorithms using C++.
				\item \textbf{Participation, IITU Robocon 2016} Built robots based on Arduino. Implemented height detection and object laying mechanism using C++.
				\item \textbf{1st prize, IV open competition of Almaty on technical projects} Awarded 1st prize for MathSnake project.
				\item \textbf{3rd prize, Almaty Legal Hackathon} Awarded 3rd prize for LawyerFinder Project.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Techologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
        \item Most Experienced: JavaScript, TypeScript, Node.js
        \item Some Experience: C++, Java, Python, Oracle SQL, Bash
        \item Familiar with: C, Scala, Vue
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
\end{document}
